### 2018-03-27 Paper/jaccardbaetica.tex
add new changes introduction

% Debate
The discussion about the production processes in Baetican area due to the lack of written sources
In archaeology, this debate has been widely studied in the last centuries (CITAR). Despite this knowledge the application of new methodology to understand the Roman trade has allowed us to deal with the complexity of Roman Market combined with the archaeological evidence \citep{orengo_seeds_2016,brughmans_roman_2016,coto-sarmiento_maria_bayesian_????}. Specifically, our work pretend to detect economic processes in a microescala focused in a commercial product from a specific province \citep{isaksen_network_2006}.

>>>>

% Debate
Despite Roman studies have widely discussed in the last centuries, the knowledge about the production processes is still under debate mostly due to the lack of written sources (CAMBIAR PORQUE LO REPITO OCHENTA VECES). The application of different approaches combined with the archaeological evidence has allowed us partly to deal with the complexity of understanding the Roman trade \citep{orengo_seeds_2016,brughmans_roman_2016,coto-sarmiento_maria_bayesian_????}. Specifically, our work pretend to detect economic processes in a microescala focuses on a commercial product from a specific province \citep{isaksen_network_2006}.
